% Acknowledgements

\pdfbookmark[1]{Acknowledgements}{Acknowledgements} % Bookmark name visible in a PDF viewer

\begin{flushright}{\slshape    
In other words, the rule about great scientific advances is that to \\ 
make them you have to break the rules. Nobody has ever won a Nobel Prize \\ 
doing what they’re told, or even by following someone else’s blueprints.} \\ \medskip
---{Joichi Ito, Director of the MIT Media Lab}
\end{flushright}

\bigskip

% “In other words, the rule about great scientific advances is that to  by  In” 
% ― Joichi Ito, Whiplash: How to Survive Our Faster Future

%----------------------------------------------------------------------------------------

\begingroup

\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax

\chapter*{Acknowledgements}

First of all, thank you \textbf{Kent Larson} for this amazing opportunity. Your decision of letting me in the City Science group opened my eyes and showed me worlds that I could not even imagine. \bigskip

I am enormously grateful to \textbf{Michael}, \textbf{Abhishek} and \textbf{Phil} for their leadership of the mobility team and for taking me in without hesitation. Thanks to \textbf{Jerry} for all these months full of great moments and hard work side by side until very late hours. To \textbf{Justin, Luke} for all those lessons and and fun moments. To my Taiwanese family \textbf{Ting--Kai and Frank} for teaching me, for helping me and for welcoming me in your wonderful country.\bigskip

To \textbf{Luis} and \textbf{Azucena} for all the invaluable help these months, for all those pieces of advice, for everything in general. And this gratefulness is extended to the whole City Science family: \textbf{Ana, Andr\'es, Ariel, Arnaud, Carson, Chrisoula, Jason, Laya, Lucas, Maggie, Markus, Mary, Nina, Roonan, Ryan, Thomas and Yasushi}. \bigskip

To \textbf{Jose} and \textbf{Eduardo}, for those great talks about every subject imaginable and lessons to become a better researcher.\bigskip

Many thanks to \textbf{Tecnun} for nominating me to go to these amazing place and all those professors that throughout these 6 years have inspired me and helped me become a better engineer and person. \bigskip

To my family, my parents, my friends here and there, for their support both emotional and finantial. And specially to you, \textbf{I}...\bigskip

\textsc{Thank you All!}
\endgroup